---
title: "R Notebook"
output: html_notebook
---

```{r}
# Packages for below analysis 
library(randomForest)
library(dplyr)
library(tidyr)
```


```{r}
# Finds the Single Ladies Frontier (not restricted to just first round; this is why "unmatched" is a required variable)
findSLF <- function(m, unmatched, n =n, current = rep(n,n)){
  SLF <- 1:n
  for(i in 1:n){
    j = current[i]
    while(!(m[i,j] %in% unmatched)){
      j=j-1
    }
    SLF[i]<-j
  }
  SLF
}

# Woman's rank by each man
popularity <- function(m, n=n){
  pop <- 1:n
  for(i in 1:n){
    pop[i] <- which(m[i,] == "girl-1")
  }
  pop
}
```




```{r}
# resultIndeces are: matched in first iteration, men proposing outcome for w1, optimal outcome, able to cheat
createData <- function(file, n, resultIndices = c(83, 108, 116, 117), changeFileName = "N"){
  # Read in the simulation file
sims <- read.csv(file)
n <- n 
nsamples <- nrow(sims)

# Turn men preferences into matrices
menprefs <- list(matrix(sims[1, 2:(n^2+n+1)], nrow = n, byrow = T)[,2:(n+1)])
for(i in 2:nsamples){
  menprefs[[i]] <- matrix(sims[i, 2:(n^2+n+1)], nrow = n, byrow = T)[,2:(n+1)]
}
  
print(menprefs)
# This section creates a matrix for the SLF and popularity plus calculations for single ladies in the first round and initial matching of woman (if exists)
SLF <- matrix(rep(0, n*nsamples), nrow =nsamples)
pop <- matrix(rep(0, n*nsamples), nrow =nsamples)
boys <- unlist(sapply(1:n, function(x){paste0("boy-",x)}))
girls <- unlist(sapply(1:n, function(x){paste0("girl-",x)}))
rnd1SL <- 1:nsamples
rnd1w1Match <- 1:nsamples
for(i in 1:nsamples){
  rnd1 <- unlist(menprefs[[i]][,1])
  rnd1w1Match[i] <- min(which(rnd1 == girls[1]), n+1)
  unmatched <- girls[which(!(girls %in% rnd1))]
  rnd1SL[i] <- length(unmatched)
  pop[i,] <- popularity(menprefs[[i]], n)
  if(length(unmatched)>0){
  SLF[i,] <- findSLF(menprefs[[i]], unmatched, n)}
  else{SLF[i,] <- rep(0,n)}
}

# Builds actual data frame for analysis
df <- data.frame(Index = 1:nsamples)
df$n <- rep(n, nsamples)
df$rnd1_is_matched <- as.integer(sims[,resultIndices[1]] =="Yes") 
df$rnd1_SL <- rnd1SL
df$rnd1_match_rank <- rnd1w1Match
df$pop1 <- pop[,1]
df$meanPop <- rowMeans(pop)
df$meanSLF <- rowMeans(SLF)
df$Y <- as.integer(sims[,resultIndices[4]] =="Yes") 
df$result <- sims[,resultIndices[3]] 
df$improvement <- sims[,resultIndices[2]] - sims[,resultIndices[3]]

SLFm <- 1:nsamples
SLFb <- 1:nsamples
for(i in 1:nsamples){
  dfTemp <- data.frame(x = 1:n, y = unname(as.matrix(SLF[i,])))
  modTemp <- lm(y ~ x, dfTemp)
  SLFm[i] <- modTemp$coefficients[2] 
  SLFb[i] <- modTemp$coefficients[1] 
}


# All analysis on attainable (to different degrees) men
attainableM <- matrix(as.integer(pop < SLF), ncol = n)
betterThanCurrent <- matrix(rep(1, n*nsamples), ncol=n)
for(i in 1:n){
  for(j in 1:nsamples)
    if(df$rnd1_match_rank[j]<=i){betterThanCurrent[j,i] <- 0}
}
attainableM <- attainableM*betterThanCurrent
attainableM2 <- matrix(as.integer(pop < (SLF-1)), ncol = n)


numMAttainable <- rowSums(attainableM)
numM2Attainable <- rowSums(attainableM2)

meanPopM <- rowSums(pop * attainableM)/numMAttainable
meanPopM2 <- rowSums(pop * attainableM2)/numM2Attainable

rankings <- rep(1:5, nsamples, byrow = T) * attainableM

meanPopM <- rowSums(rankings)/numMAttainable
rankings[rankings == 0] <- n+1
maxMAttainable <- apply(rankings, 1, min)
SLFmin <- apply(unname(SLF), 1, min)

df$numMAttainable <- numMAttainable
df$numM2Attainable <- numM2Attainable
df$SLFm <- SLFm
df$SLFb <- SLFb

df$rankm <- rowMeans(abs(pop - rep(1:n, nsamples, byrow = T)))
df$meanPopM <- meanPopM
df$meanPopM2 <- meanPopM2
df$maxMAttainable <- maxMAttainable
df$SLFmin <- SLFmin

breaks <- c(1, ceiling(n/4), ceiling(n/2), n)
if(breaks[1] == breaks[2]){df$poph <- pop[,breaks[1]:breaks[2]]}
else{df$poph <- rowMeans(pop[,breaks[1]:breaks[2]])}

if(breaks[2] == breaks[3]){df$popm <- pop[,breaks[2]:breaks[3]]}
else{df$popm <- rowMeans(pop[,breaks[2]:breaks[3]])}

if(breaks[3] == breaks[4]){df$popl <- pop[,breaks[3]:breaks[4]]}
else{df$popl <- rowMeans(pop[,breaks[3]:breaks[4]])}


df[is.na(df)] <- n+1



if(changeFileName == "N"){
write.csv(df, paste0("df",n,".csv"))}
else{
  write.csv(df, paste0("df", changeFileName,n,".csv"))
}

# The reason for returning menprefs here was for a few very specific instances where I found it useful to have them separately
# The fact that this is the return value has pretty much nothing to do with the actual purpose of this function ;)
menprefs

}


```


Column labels:

0 - 59 -> preferences 
60 -69 -> matches when M propose to W 
70 -> total iterations 
71 - 80 -> Matches in first iteration 
81 -> is G1 matched in first iteration 
82 - 95 -> list of men proposed to G1 in order and if she accept or not 
96 - 105 -> matches when women propose to men 
106 -> index G1 achieved when Men proposed 
107 -> index G1 achieved when Women proposed 
108 -> is G1 preference already optimal 
109 - 113 -> optimal preference order 
114 -> on optimal preference best achieved index 
115 -> Has result improved by manipulating


resultIndeces are: matched in first iteration, men proposing outcome for w1, optimal outcome, able to cheat

```{r}
# This creates all of the relevant data files from the Python-generated data
createData(file = "dataframe5.csv", n=5, resultIndices = c(83, 108, 116, 117))
createData(file = "dataframe10.csv", n=10, resultIndices = c(263, 306, 319, 320))
createData(file = "dataframe15.csv", n=15, resultIndices = c(543, 604, 622, 623))
createDataR(file = "dataframe5.csv", n=5, resultIndices = c(83, 108, 116, 117))
createDataR(file = "dataframe10.csv", n=10, resultIndices = c(263, 306, 319, 320))
createDataR(file = "dataframe15.csv", n=15, resultIndices = c(543, 604, 622, 623))
```






# Analysis Section

```{r}
# Runs the random forest model
runRF <- function(df, independent = "Y", numMan = 2000, numNMan = 2000){
if(independent == "Y"){
  dfMan <- df[which(df$Y==1),]
dfNMan <- df[which(df$Y==0),]

tryTest <- rbind(dfMan[1:numMan,], dfNMan[1:numNMan,])
mod <- randomForest(as.factor(Y)~., data=tryTest, importance=TRUE,
                        proximity=TRUE, )}

  
  
  if(independent == "result"){
mod <- randomForest(result~., data=df, importance=TRUE,
                        proximity=TRUE)}

  
  
  if(independent == "improvement"){
mod <- randomForest(improvement~., data=df, importance=TRUE,
                        proximity=TRUE)}

mod
}
```

```{r}
# Generates some result plots from testing models by factors
makePrettyPlots <- function(mod, data, predVals, truth){
  varImpPlot(mod)
  
  predictions <- predict(mod, predVals)
predictionsprob <- predict(mod, predVals, type = "prob")

results <- data.frame(Truth = truth, probs = predictionsprob, predictions = predictions)
par(mfrow = c(2,2))
hist(results$probs.0[which(results$Truth==0)], main = "prob 0 when 0")
hist(results$probs.0[which(results$Truth==1)], main = "prob 0 when 1")
hist(results$probs.1[which(results$Truth==1)], main  = "prob 1 when 1")
hist(results$probs.1[which(results$Truth==0)], main  = "prob 1 when 0")

table(observed =  truth, predicted = predictions)

}

```


```{r}
# Generates several more prediction results; named for the table binned by num bins
binnedTable <- function(num, mod, predVals, truth){
    predictions <- predict(mod, predVals)
predictionsprob <- predict(mod, predVals, type = "prob")

results <- data.frame(Truth = truth, probs = predictionsprob, predictions = predictions)
c1 <- (0:(num-1))/num
c2 <- (1:num)/num

means <- sapply(1:num, function(x){mean(results$Truth[which(results$probs.1>=c1[x] & results$probs.1<c2[x])]) })
manipulable <- sapply(1:num, function(x){sum(results$Truth[which(results$probs.1>=c1[x] & results$probs.1<c2[x])]) })
labels <- sapply(1:num, function(x){paste0(c1[x], "-",c2[x])})

means <- c(means, mean(truth))
manipulable <- c(manipulable, sum(truth))
labels <- c(labels, "Total")

knitr::kable(matrix(c(means, manipulable), nrow = 2, byrow = T), col.names = labels, digits = 2)

}

```



```{r}
# This was a test only based on the n=5 case
data <- read.csv("df5.csv")
mod <- runRF(data[,-c(1,2,3,11,12)], "Y")
makePrettyPlots(mod, data, data[,-c(1,2,3,10,11,12)], data$Y)
binnedTable(10,mod,data[80000:100000,-c(1,2,3,10,11,12)], data$Y[80000:100000])
```


```{r}
# Testing based on only n=10
data10 <- read.csv("df10.csv")
mod10 <- runRF(data10[,-c(1,2,3,11,12)], "Y")
makePrettyPlots(mod10, data10, data10[40000:50000,-c(1,2,3,10,11,12)], data10$Y[40000:50000])
binnedTable(10,mod10,data10[40000:50000,-c(1,2,3,10,11,12)], data10$Y[40000:50000])
```



```{r}
# Testing based only on n=15
data15 <- read.csv("df15.csv")
mod15 <- runRF(data15[,-c(1,2,3,11,12)], "Y")
makePrettyPlots(mod15, data15, data15[29325:30000,-c(1,2,3,10,11,12)], data15$Y[29325:30000])
binnedTable(10,mod15,data15[29325:30000,-c(1,2,3,10,11,12)], data15$Y[29325:30000])
```

```{r}
# Actual analysis for the combinded n=5,10,15 case

dfMan5 <- data[which(data$Y==1),]
dfNMan5 <- data[which(data$Y==0),]
dfMan10 <- data10[which(data10$Y==1),]
dfNMan10 <- data10[which(data10$Y==0),]
dfMan15 <- data15[which(data15$Y==1),]
dfNMan15 <- data15[which(data15$Y==0),]

dataAll <- rbind(data, data10, data15)
dataAll <- rbind(dfMan5[1:2000,], dfNMan5[1:2000,], dfMan10[1:2000,], dfNMan10[1:2000,], dfMan15[1:2000,], dfNMan15[1:2000,])
modA <- runRF(dataAll[,-c(1,2,11,12)], "Y", 6000, 6000)
testData <- rbind(data[90001:100000,],data10[40001:50000,],data115[1:10000,])
 makePrettyPlots(modA, testData, testData[,-c(1,2,10,11,12)], testData$Y)
 binnedTable(10,modA,testData[,-c(1,2,10,11,12)], testData$Y)
```










# Expected value of result

```{r}
# n=5 only test
data<- read.csv("df5.csv")
modR5 <- runRF(data[1:10000,-c(1,2,10,12)], "result")
modR5
```

```{r}
# Altered version of make Pretty Plots dropping things that don't make sense when using regression
makePrettyPlotsR <- function(mod, data, predVals, truth){
  varImpPlot(mod)
  
  predictions <- predict(mod, predVals)
# predictionsprob <- predict(mod, predVals, type = "prob")

# results <- data.frame(Truth = truth, probs = predictionsprob, predictions = predictions)
# par(mfrow = c(2,2))
# hist(results$probs.0[which(results$Truth==0)], main = "prob 0 when 0")
# hist(results$probs.0[which(results$Truth==1)], main = "prob 0 when 1")
# hist(results$probs.1[which(results$Truth==1)], main  = "prob 1 when 1")
# hist(results$probs.1[which(results$Truth==0)], main  = "prob 1 when 0")

#table(observed =  truth, predicted = predictions)

}

```


```{r}
# Test with n=10
data10<- read.csv("df10.csv")
modR10 <- runRF(data10[1:10000,-c(1,2,10,12)], "result")
modR10
```

```{r}
# Test with n=15
data15<- read.csv("df15.csv")
modR15 <- runRF(data15[1:10000,-c(1,2,10,12)], "result")
modR15
```


```{r}
# Version of binnedTable that works for regression; focuses on errors instead of bins
binnedTableR <- function(num, mod, predVals, truth){
    predictions <- predict(mod, predVals)
    print(summary(predictions - truth))
    print(summary(round(predictions,0) - truth))
    
    c(mean((predictions-truth)^2), mean((round(predictions,0)-truth)^2))
    
#predictionsprob <- predict(mod, predVals, type = "prob")

# results <- data.frame(Truth = truth,  predictions = predictions)
# c1 <- (0:(num-1))/num
# c2 <- (1:num)/num
# 
# means <- sapply(1:num, function(x){mean(results$Truth[which(results$probs.1>=c1[x] & results$probs.1<c2[x])]) })
# manipulable <- sapply(1:num, function(x){sum(results$Truth[which(results$probs.1>=c1[x] & results$probs.1<c2[x])]) })
# labels <- sapply(1:num, function(x){paste0(c1[x], "-",c2[x])})
# 
# means <- c(means, mean(truth))
# manipulable <- c(manipulable, sum(truth))
# labels <- c(labels, "Total")
# 
# knitr::kable(matrix(c(means, manipulable), nrow = 2, byrow = T), col.names = labels, digits = 2)

}
# binnedTable(20, results)
# binnedTable(10, results)
# binnedTable(5, results)
```




```{r}
# n=5 results
binnedTableR(10, modR5, data[20000:30000,-c(1,2,10,11,12)], data$result[20000:30000])
```
```{r}
# n=10 results
binnedTableR(10, modR10, data10[20000:30000,-c(1,2,10,11,12)], data10$result[20000:30000])
```
```{r}
#n=15 results
binnedTableR(10, modR15, data15[20000:30000,-c(1,2,10,11,12)], data15$result[20000:30000])
```

```{r}
# Regression version with n = 5, 10, and 15 
# Note that this is still just testing with the original predictors
dataA<- rbind(data[1:2000,], data10[1:2000,], data15[1:2000,])
modRA <- runRF(dataA[,-c(1,2,10,12)], "result")
modRA
```

```{r}
# For comparison
varImpPlot(modR5)
varImpPlot(modR10)
varImpPlot(modR15)
varImpPlot(modRA)
```





# Results formulation with custom data

```{r}
# resultIndeces are: matched in first iteration, men proposing outcome for w1, optimal outcome, able to cheat
createDataR <- function(file, n, resultIndices = c(83, 108, 116, 117), changeFileName = "N"){
  # Read in the simulation file
sims <- read.csv(file)

nsamples <- nrow(sims)

# Turn men preferences into matrices
menprefs <- list(matrix(sims[1, 2:(n^2+n+1)], nrow = n, byrow = T)[,2:(n+1)])
for(i in 2:nsamples){
  menprefs[[i]] <- matrix(sims[i, 2:(n^2+n+1)], nrow = n, byrow = T)[,2:(n+1)]
}
  

# This section creates a matrix for the SLF and popularity plus calculations for single ladies in the first round and initial matching of woman (if exists)
SLF <- matrix(rep(0, n*nsamples), nrow =nsamples)
pop <- matrix(rep(0, n*nsamples), nrow =nsamples)
boys <- unlist(sapply(1:n, function(x){paste0("boy-",x)}))
girls <- unlist(sapply(1:n, function(x){paste0("girl-",x)}))
rnd1SL <- 1:nsamples
rnd1w1Match <- 1:nsamples
for(i in 1:nsamples){
  rnd1 <- unlist(menprefs[[i]][,1])
  rnd1w1Match[i] <- min(which(rnd1 == girls[1]), n+1)
  unmatched <- girls[which(!(girls %in% rnd1))]
  rnd1SL[i] <- length(unmatched)
  pop[i,] <- popularity(menprefs[[i]], n)
  if(length(unmatched)>0){
  SLF[i,] <- findSLF(menprefs[[i]], unmatched, n)}
  else{SLF[i,] <- rep(0,n)}
}

# Builds actual data frame for analysis
df <- data.frame(Index = 1:nsamples)
df$n <- rep(n, nsamples)
df$rnd1_is_matched <- as.integer(sims[,resultIndices[1]] =="Yes") 
df$rnd1_SL <- rnd1SL
df$rnd1_match_rank <- rnd1w1Match
df$pop1 <- pop[,1]
df$meanPop <- rowMeans(pop)
df$meanSLF <- rowMeans(SLF)
df$Y <- as.integer(sims[,resultIndices[4]] =="Yes") 
df$result <- sims[,resultIndices[3]] 
df$improvement <- sims[,resultIndices[2]] - sims[,resultIndices[3]]

SLFm <- 1:nsamples
SLFb <- 1:nsamples
for(i in 1:nsamples){
  dfTemp <- data.frame(x = 1:n, y = unname(as.matrix(SLF[i,])))
  #dfTemp$y <- t(as.matrix(df[i,11:15]))
  modTemp <- lm(y ~ x, dfTemp)
  SLFm[i] <- modTemp$coefficients[2] 
  SLFb[i] <- modTemp$coefficients[1] 
}



attainableM <- matrix(as.integer(pop <= SLF), ncol = n)
betterThanCurrent <- matrix(rep(1, n*nsamples), ncol=n)
for(i in 1:n){
  for(j in 1:nsamples)
    if(df$rnd1_match_rank[j]<i){betterThanCurrent[j,i] <- 0}
}
attainableM <- attainableM*betterThanCurrent
attainable <- matrix(as.integer(pop <= SLF), ncol = n)


numMAttainable <- rowSums(attainableM)
numAttainable <- rowSums(attainable)

meanPopM <- rowSums(pop * attainableM)/numMAttainable
meanPop <- rowSums(pop * attainable)/numAttainable

rankings <- rep(1:5, nsamples, byrow = T) * attainableM

meanPopM <- rowSums(rankings)/numMAttainable
rankings[rankings == 0] <- n+1
maxMAttainable <- apply(rankings, 1, min)
SLFmin <- apply(unname(SLF), 1, min)

df$numMAttainable <- numMAttainable
df$numAttainable <- numAttainable
df$SLFm <- SLFm
df$SLFb <- SLFb

df$rankm <- rowMeans(abs(pop - rep(1:n, nsamples, byrow = T)))
df$meanPopM <- meanPopM
df$meanPop <- meanPop
df$maxMAttainable <- maxMAttainable
df$SLFmin <- SLFmin

breaks <- c(1, ceiling(n/4), ceiling(n/2), n)
if(breaks[1] == breaks[2]){df$poph <- pop[,breaks[1]:breaks[2]]}
else{df$poph <- rowMeans(pop[,breaks[1]:breaks[2]])}

if(breaks[2] == breaks[3]){df$popm <- pop[,breaks[2]:breaks[3]]}
else{df$popm <- rowMeans(pop[,breaks[2]:breaks[3]])}

if(breaks[3] == breaks[4]){df$popl <- pop[,breaks[3]:breaks[4]]}
else{df$popl <- rowMeans(pop[,breaks[3]:breaks[4]])}




df[is.na(df)] <- n+1



if(changeFileName == "N"){
write.csv(df, paste0("df",n,"R.csv"))}
else{
  write.csv(df, paste0("df", changeFileName,n,"R.csv"))
}


}


```



```{r}
data5R<- read.csv("df5R.csv")
data10R<- read.csv("df10R.csv")
data15R<- read.csv("df15R.csv")
```



```{r}
# Create new data files
createDataR(file = "dataframe5.csv", n=5, resultIndices = c(83, 108, 116, 117))
createDataR(file = "dataframe10.csv", n=10, resultIndices = c(263, 306, 319, 320))
createDataR(file = "dataframe15.csv", n=15, resultIndices = c(543, 604, 622, 623))
```

resultIndeces are: matched in first iteration, men proposing outcome for w1, optimal outcome, able to cheat


```{r}
# At this point, we simulated more n=15 cases in order to have a bigger sample of manipulable ones
createData(file = "dataframe15_1.csv", n=15, resultIndices = c(543, 604, 622, 623), changeFileName = "1")
createDataR(file = "dataframe15_1.csv", n=15, resultIndices = c(543, 604, 622, 623), changeFileName = "1")

data115 <- read.csv("df115.csv")
data115R <- read.csv("df115R.csv")
```


```{r}
# Predicting outcomes with regression
dataAR<- rbind(data5R[1:5000,], data10R[1:5000,], data15R[1:5000,])
modRAR <- runRF(dataAR[,-c(1,2,10,12)], "result")
modRAR
```

```{r}
# Predicting outcomes with results as ordered factors
# I casually love that All, Results, factor abbreviates to ARf
dataARf<- dataAR
dataARf$result <- as.ordered(as.factor(dataARf$result))
modRARf <- runRF(dataARf[,-c(1,2,10,12)], "result")
modRARf
```


```{r}
# Testing 
test <- rbind(data5R[5001:15000,], data10R[5001:15000,], data15R[5001:15000,])
makePrettyPlotsR(mod = modRAR, data = dataRAR, predVals = test[,-c(1,2,10,11,12)], truth = test$result)
binnedTableR(mod = modRAR, predVals = test[,-c(1,2,10,11,12)], truth = test$result)
```


```{r}
# Comparisons between factor and regression version
makePrettyPlots(mod = modRARf, data = dataRAR, predVals = test[,-c(1,2,10,11,12)], truth = test$result)
predictedVals <- as.data.frame(predict(modRARf, test[,-c(1,2,10,11,12)], type = "prob"))
predictedVals$Truth <- test$result
predictedVals$errorR <- predict(modRAR, test[,-c(1,2,10,11,12)]) - test$result
gP <- predictedVals %>% group_by(Truth) %>% summarize_all(mean)
predictedValsV <- as.data.frame(predict(modRARf, test[,-c(1,2,10,11,12)]))
predictedValsV$Truth <- test$result
predictedValsV$error <- as.integer(predictedValsV$`predict(modRARf, test[, -c(1, 2, 10, 11, 12)])`) - as.integer(predictedValsV$Truth)
gPf <- predictedValsV %>% group_by(Truth) %>% summarize_all(mean)
mean(predictedValsV$error^2)
gP$errorR
gPf$error
```


# Robustness checks based on numbers of single ladies in the first period

This section is slightly outdated in that we later realized that we may not be able to fully reduce the problem to a single single lady without further querying. I kept it here since this still does demonstrate some degree of robustness in our methods and could be indirectly argued to be beneficial in demonstrating that we trained on "enough" data.

```{r}
data1SL <- rbind(data5R[data5R$rnd1_SL ==1, ], data10R[data10R$rnd1_SL ==1, ], data15R[data15R$rnd1_SL ==1, ], data115R[data115R$rnd1_SL ==1, ])
```


```{r}
modsl1 <- runRF(data1SL[1:10000,-c(1,2,10,12)], "result")
modsl2 <- runRF(data5R[1:10000,-c(1,2,10,12)], "result")
```

```{r}
modsl2 <- runRF(data5R[1:10000,], "result")
```

```{r}
modsl1
modsl2
```

```{r}
makePrettyPlotsR(mod = modsl1, data = dataAR, predVals = data1SL[10001:20000,-c(1,2,10,11,12)], truth = data1SL$result[10001:20000])
binnedTableR(mod = modsl1, predVals = data1SL[10001:20000,-c(1,2,10,11,12)], truth = data1SL$result[10001:20000])
```

```{r}
makePrettyPlotsR(mod = modsl2, data = dataAR, predVals = data1SL[10001:20000,-c(1,2,10,11,12)], truth = data1SL$result[10001:20000])
binnedTableR(mod = modsl2, predVals = data1SL[10001:20000,-c(1,2,10,11,12)], truth = data1SL$result[10001:20000])
```

```{r}
 binnedTable(10,modA,testData[,-c(1,2,10,11,12)], testData$Y)
 binnedTable(5,modA,testData[,-c(1,2,10,11,12)], testData$Y)
  binnedTable(20,modA,testData[,-c(1,2,10,11,12)], testData$Y)
```



# Creating the examples from our proposal

```{r}
mprefs <- createData("TestData.csv", 5)
createDataR("TestData.csv", 5)
```

```{r}
sims <- read.csv("TestData.csv")
n <- 5
nsamples <- nrow(sims)

# Turn men preferences into matrices
womenprefs <- list(matrix(sims[1, ((n^2+n+1)+2):(2*(n^2+n+1))], nrow = n, byrow = T)[,2:(n+1)])
for(i in 2:nsamples){
  womenprefs[[i]] <- matrix(sims[i, ((n^2+n+1)+1):(2*(n^2+n+1)-1)], nrow = n, byrow = T)[,2:(n+1)]
}

womenprefs
```

```{r}
testingData <- read.csv("dfT5.csv")
testingDataR <- read.csv("dfT5R.csv")
```

Teo's example is 1, one with 2 single ladies (but doesn't manipulate) is 2 (and is the seventh to last one from dataframe5)

```{r}
predict(modA, testingData[1,-c(1,2,10,11,12)], type = "prob")
predict(modA, testingData[2,-c(1,2,10,11,12)], type = "prob")
predict(modA, testingData[3,-c(1,2,10,11,12)], type = "prob")
predict(modRAR, testingDataR[4,-c(1,2,10,11,12)])
predict(modRAR, testingDataR[5,-c(1,2,10,11,12)])
predict(modRAR, testingDataR[6,-c(1,2,10,11,12)])
```
4 = Teo's example (currently matched with 5 after rejecting 4)
5 = case where kept 4 instead of 3
6 = case where kept 5 instead of 3


